---
title: "Reported Hours"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r global, include=FALSE}

# load package
library(tidyverse) # include tidyverse, ggplot2, tibble, tidyr, readr, purrr, dplyr, stringr, forcats
library(readxl)    # read excel
library(lubridate) # convert date

# load data
data <- read_excel("ataaps_example_10Apr20.xlsx", sheet = "DATA", col_types = "text")

# clean and subset data
data.2 <-  
    data %>% 
      mutate(CY = as.numeric(substr(Year,8,11))) %>%          # create new variable: CY
      mutate(hours = as.numeric(Hours.Charged)) %>%           # convert hours to numeric
      mutate(CM = case_when(Month=="JAN" ~1,                  # convert month to numeric
                            Month=="FEB" ~2,
                            Month=="MAR" ~3,
                            Month=="APR" ~4,
                            Month=="MAY" ~5,
                            Month=="JUN" ~6,
                            Month=="JUL" ~7,
                            Month=="AUG" ~8,
                            Month=="SEP" ~9,
                            Month=="OCT" ~10,
                            Month=="NOV" ~11,
                            Month=="DEC" ~12),
              CD = 1) %>%                                     # create day of month
      mutate(date=make_date(CY,CM,CD)) %>%                    # combine year, month, day to date
      select(date,                                            # subset the dataset to few variables
             Employee.Name,
             Rating.Year,
             WBS.Group.Name,
             Job.Order.Type.Description,
             WBS.Group.Category,
             hours) 

```

# Overall

## Column {.sidebar}

**BACKGROUND:** 

This dashboard was developed by Katherine Schaughency. The intent was to use the workload data to practice her R skill using tidyverse and flexdashboard. 

**DASHBOARD:** 

This dashboard summarizes reported labor hours for each project/non-project from Dec 2017 to Mar 2020. 

**USER INPUTS:**

```{r input1.1}

selectInput(inputId = "name", 
            label = "Name of the Employee:",
            choices = c("DOE, JOHN"),
            selected = "DOE, JOHN")

selectInput(inputId = "wbs.type",
            label = "Billable Type:",
            choices = c("Project", "Non-Project"),
            selected = "Project")

```


## Column {.tabset} 

### Plot

```{r output1.1}

renderPlot({

       data.2 %>%                               
          filter(Employee.Name == input$name) %>% 
          filter(WBS.Group.Category == input$wbs.type) %>% 
    
          group_by(date, WBS.Group.Name) %>% 
          summarize(total.hours = sum(hours)) %>%  
  
          ggplot(aes(x=date,
                     y=reorder(WBS.Group.Name, desc(WBS.Group.Name)),
                     size=total.hours,
                     color=WBS.Group.Name)) +
          geom_point(alpha=0.5) +
          scale_y_discrete(labels = function(k) str_wrap(k, width = 20)) +
          scale_size(range = c(.1, 24), name="Reported Hours") +
          ggtitle("Monthly Hours Worked on Each Project") +
          ylab("Project Name") +
          xlab("Calendar Year & Month")  

}, height = "auto", width = "auto")

```

### Summary Table

```{r output1.2}

renderTable({

      data.2 %>%                               
          filter(Employee.Name == input$name) %>% 
          #filter(Rating.Year == input$rate.year) %>% 
          filter(WBS.Group.Category == input$wbs.type) %>% 
    
          group_by(WBS.Group.Name) %>% 
          summarize(total.hours = sum(hours)) %>% 
    
          arrange(desc(total.hours), .by_group = TRUE)

})

```

# Rating Period

## Column {.sidebar}

**BACKGROUND:** 

This dashboard was developed by Katherine Schaughency. The intent was to use the workload data to practice her R skill using tidyverse and flexdashboard. 

**DASHBOARD:** 

This dashboard summarizes reported labor hours for each project/non-project from Dec 2017 to Mar 2020. 

**USER INPUTS:**

```{r input2.1}

selectInput(inputId = "name.2", 
            label = "Name of the Employee:",
            choices = c("DOE, JOHN"),
            selected = "DOE, JOHN")

selectInput(inputId = "wbs.type.2",
            label = "Billable Type:",
            choices = c("Project", "Non-Project"),
            selected = "Project")

selectInput(inputId = "rate.year",
           label = "Rating Year:",
           choices = c("2017-2018","2018-2019","2019-2020"),
           selected = "2019-2020")

```


## Column {.tabset} 

### Plot

```{r output2.1}

renderPlot({

       data.2 %>%                               
          filter(Employee.Name == input$name.2) %>% 
          filter(Rating.Year == input$rate.year) %>% 
          filter(WBS.Group.Category == input$wbs.type.2) %>% 
    
          group_by(date, WBS.Group.Name) %>% 
          summarize(total.hours = sum(hours)) %>%  
  
          ggplot(aes(x=date,
                     y=reorder(WBS.Group.Name, desc(WBS.Group.Name)),
                     size=total.hours,
                     color=WBS.Group.Name)) +
          geom_point(alpha=0.5) +
          scale_y_discrete(labels = function(k) str_wrap(k, width = 20)) +
          scale_size(range = c(.1, 24), name="Reported Hours") +
          ggtitle("Monthly Hours Worked on Each Project") +
          ylab("Project Name") +
          xlab("Calendar Year & Month")  

}, height = "auto", width = "auto")

```

### Summary Table

```{r output2.2}

renderTable({

      data.2 %>%                               
          filter(Employee.Name == input$name.2) %>% 
          filter(Rating.Year == input$rate.year) %>% 
          filter(WBS.Group.Category == input$wbs.type.2) %>% 
    
          group_by(WBS.Group.Name) %>% 
          summarize(total.hours = sum(hours)) %>% 
    
          arrange(desc(total.hours), .by_group = TRUE)

})

```
